---Preparation---

gganimate installing
```{r}
if(!require(devtools)) install.packages("devtools")
devtools::install_github("dgrtwo/gganimate")
#or install.packages('gganimate')
install.packages("gapminder") #for data use
```
ImageMagick installing (In terminal)
$ cd /usr/local
$ git reset --hard FETCH_HEAD
$ brew install imagemagick
#You may need to install homebrew first... ;)


---Simple animation---

Plot the variable lifeExp (life expectancy at birth) by the variable gdpPercap (GDP per capita).
Make animation by year using the aesthetic frame = year.
```{r}
# Load required package
library(gapminder)
library(ggplot2)
library(gganimate)
# Basic scatter plot
mapping <- aes(x = gdpPercap, y = lifeExp, 
               size = pop, color = continent,
               frame = year) 
p <- ggplot(gapminder, mapping = mapping) +
  geom_point() +
  scale_x_log10()
p
# Animate
gganimate(p, frame = continent) 

#To animate across continent, in mapping use frame = continent.
#For faster animation use the option interval, for example interval = 0.2
```

---Save the animation---
Allowed format: an GIF, video, or an animated webpage.
```{r}
gganimate(p, "output.gif")
gganimate(p, "output.mp4")
gganimate(p, "output.swf")
gganimate(p, "output.html")
```
System requirement: ffmpeg and ImageMagick drivers should be installed on your computer.


---Customization---

Animate some of the plot layers by highlighting particular points:
```{r}
p2 <- ggplot(gapminder, aes(gdpPercap, lifeExp, size = pop)) +
  geom_point() +
  geom_point(aes(frame = year), color = "red") +
  scale_x_log10()
gganimate(p2)
```

```{r}
# Cumulative layer using the aesthetic cumulative = TRUE.
p3 <- ggplot(gapminder, aes(gdpPercap, lifeExp, frame = year)) +
  geom_path(aes(cumulative = TRUE, group = country)) +
  scale_x_log10() +
  facet_wrap(~continent)
gganimate(p3)
```



```{r}
## Import packages ##
library(ggplot2)
library(dplyr)
library(tidyr)
library(purrr)
library(animation)
library(gganimate)
 
## Function to evaluate Beta pdf for a vector of values ##
calc_beta = function(alpha, beta){
  x = seq(0.01, 0.99, 0.01)
  densityf = dbeta(x, shape = alpha, shape2 = beta)
  return(data_frame(x, densityf))
}
 
## Create data frame with evaluation of Beta pdf for different combinations of alpha and beta ##
alpha = c(0.1, 0.5, 1:5, 10)
beta = c(0.5, 1, 2, 5)
 
## Create data frame ## 
# Couldn't get the pipe operator to properly show up in WordPress :-(
df = expand.grid(alpha = alpha, beta = beta)
df = group_by(df, alpha, beta) 
df = unnest(mutate(df, plotdata = map2(alpha, beta, calc_beta)))
 
## Create plot ##
p = ggplot(df, aes(x = x, y = densityf, colour = factor(alpha), group = factor(alpha))) + 
  geom_path(aes(frame = alpha, cumulative = TRUE), size = 0.5) +
  facet_wrap(~beta, 
             labeller = label_bquote(cols = beta == .(beta))) +
  ylim(c(0, 6)) +
  labs(y = expression(paste("f(x; ", alpha, ", ", beta, ")")),
       title = "Changing parameters in Beta density function") +
  scale_colour_discrete(name = expression(alpha)) +
  theme(plot.title = element_text(hjust = 0.5))
 
ani.options(interval = 0.8)
gganimate(p, title_frame = FALSE, width = 4, height = 4)
```

Reference:
http://www.sthda.com/english/articles/16-r-packages/58-gganimate-create-animations-with-ggplot2/
http://www.ggplot2-exts.org/gganimate.html